What can GitHub and Googlecode Issues tell us about Exceptions in Android?

### 2014-08-29 android-stacks.tex
changes along the paper

Such fragilities represent obstacles to the development of dependable mobile apps as well as other Java-based systems
as they share the same exception model. Although the study focused on Android opensource applications, some of the results are not restricted to this context, 
for instance: some of the unexpected wrappings were performed by Java libraries and elements (e.g. reflection library and 
the static blocks); and the undocumented runtime exceptions were also found in Java libraries besides the Android plaftorm.
The study results are relevant to: (i) Android and Java developers to familiarize common characteristics and fragilities of exception-related code 
which is the first step to help developers preventing and dealing with them; (ii) designers of languages and tools to consider ways of reducing 
such fragilities in Android and Java environments.

>>>>

Such fragilities represent obstacles to the development of dependable java-based applications as they make difficult and 
sometimes almost impossible to protect the code against the Uncaught Exceptions that lead to system crashes.
Although the study focused on Android opensource applications, some of the results are not restricted to this context, 
for instance: some of the unexpected wrappings were performed by Java libraries and elements (e.g. reflection library and 
the static blocks); and the undocumented runtime exceptions were also found in Java libraries besides the Android plaftorm.
The study results are relevant to: (i) Android and Java developers to familiarize common characteristics and fragilities of exception-related code 
which is the first step to help developers preventing and dealing with them; (ii) designers of languages and tools to consider ways of reducing 
such fragilities in Android and Java environments.
